---
title: "CBIT Project, Uganda: First steps with R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R 

This training has been conceived for the NFMS in Uganda. The specific purpose is to import, analize and report data from plantations.
To do it we use the R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:


```{r iris}
summary(iris)
```

## Including Plots

You can also embed plots, for example:

```{r widthexample, echo=FALSE}
plot(iris$Sepal.Width~iris$Sepal.Length)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Import data

"Iris" is just a default dataset, useful to do some testing.

But we want to do more today...

Let's add a new chunk of code, to do it there  are two ways, by using the keybord (Code-> Insert Chunk) or like a boss (CTRL+ALT+I)!
...but only after this line...
```{r NAME_here}

rm(list=ls())
```
ok then, let's continue.

We now need to import data, but how?
You can import several sources of dataset, xls files, csv, txt, dbf. And you can import from your laptop, from the web, from a server in your lan.

Let's start with a simple example.
Download the csv files that you find here: [NFI Dataset][1]

[1]:https://raw.githubusercontent.com/antonellosalis/R_training/master/Data_training/tree.csv

For this training (ans with R in general) it is important to be organized.

1) In your desktop, or in your working directory, create a new folder called "R_training"
2) In this folder create 2 folders "Data" and "Scripts"
3) Copy the daatset in the "Data" directory
4) Ctrl+Alt+I...that means?

>_TIP&TRICKS: Use TAB key in the script to complete for you command or paths_

```{r Import}

NFIData <- read.csv ("/home/antonello/R_projects/R_trainings/CBIT/Data/tree.csv", header=T)

head(NFIData)

```


**Congratulations! You imported successfully your first dataset**

#Before proceed: simple but useful considerations
```{r}
# Simple operations
2+3

#2+3 
#You see? If I add # to a line the operation will be ignored

2*3
2-3
2/3
2^3
2%%3
sqrt(2)
log(2)
log10(2)
log1p(2)
2+3; 2*3; log10(2)

# Help!

?log
?sqrt

#Example here the first important command:

rm(list=ls())
# Translation: rm() means remove 
#              list() mean (surprise!) list
#              ls() give us the list of all the objects in our workspace
#              This command will clean the workspace and all the objects!

# Restart the plot device
dev.off()
# Translation: "please RStudio  also clean all the graphics"
# It is recomnmended to clean the plot device and the environment in RStudio before start.
#Do you remember the boxes?
#Let's start with a small box, a variable:

A <- 3

B <- 10

A + B

A + B + 2

A <- B

# A + B + 2 = ?


C <- A + B + 2

C
```





